%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%       PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:   the name and address are centered at the top of the page 
%                               (default)
%
%   line:               the name is the left with a horizontal line then the address to
%                               the right
%
%   overlapped: the section titles overlap the body text (default)
%
%   margin:             the section titles are to the left of the body text
%
%   11pt:               use 11 point fonts instead of 10 point fonts
%
%   12pt:               use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%       NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Victor Delaplaine}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{
\\Website : web.calpoly.edu/~vdelapla/
\\LinkedIn : www.linkedin.com/in/victor-delaplaine
\\Github : www.github.com/ByVictorrr\\
}
\address{vdelapla@calpoly.edu \\(+650) 740-6691\\}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%       EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
{\sl Junior level Computer Engineering Student at Cal Poly. Inquisitive, hard-working and consistent. Looking for internship opportunities where I can apply my skills and contribute to real-world projects.}

\section{EDUCATION}
\textbf{California Polytechnic State University}, San Luis Obispo\\
{\sl Bachelor of Science (BS)}, Computer Engineering(CPE)\\
Expected June, 2020
\hfill CGPA: 3.9/4.00 

%-------------------------------------------------------------------------------
%       COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{TECHNICAL\\SKILLS}

\textbf{Programming: } Shell, C++, Java, Verilog
\\
\textbf{ Markdown :} MarkDown, LaTex, html
\\
\textbf{Familiar : } Matlab, CSS, MySQL, Regular Expressions
\\
\textbf{General : }Data Structures, Object Oriented Programming, Digital Design, Unix tools

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{San Francisco State : Machine learning lead intern \hfill{June 18 - August 18}\\}
\\
\normalfont{ I woked on an android application in java - that reads EMG signals and demodulates them into gestures, to the display. I helped with setting up the EC2 AWS server to get a working SQL base for large amounts of data need to store.}

\begin{itemize}
\item \textbf{Tools :} MySQL, teamwork, AWS, research and presenting
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/alexanderadavid/Myo-HMI-Android
\end{itemize}

\textbf{ Canada College: STEM tutor \hfill{January 18 - June 18}\\}
\\
\normalfont{I was a Math, Physics, Engineering, and Computer science tutor. \\ I loved helping student suceed, by showing them how to solve a problem step by step.}
\begin{itemize}
\item \textbf{Tools :} Teaching
\end{itemize}
\begin{itemize}
\item \textbf{Link :} https://www.canadacollege.edu/stemcenter/ 
\end{itemize}



\section{RECENT PROJECTS}

% Project 1
\employer{ByVictorrr}
\location{}
\title{\textbf{aProjector - Autofocusing Projector \hfill September 2018}}
\begin{position}
% \begin{itemize}
  The aProjector, was a invention of me and a peer, simply its a projector which projects a phones screen on the wall and autofocuses it. I used the thin lens equation as a basis to devlope a program written in C++ run on the Arduino Mega 2560. This Arudino controls the motor to turn the stepper motor a given angle needed to produce a clear image on the wall.
% \end{itemize}https://www.overleaf.com/project/5c3cda8d86f90560469d48be
\begin{itemize}
\item \textbf{Technology/Tools:} C++, LaTex
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/byvictorrr/aProjector
\end{itemize}
\end{position}



%Project 2
\employer{ByVictorrr}
\location{}
\title{\textbf{ RPI Camera EC2 Backup - Autonomous backup  \hfill December 2018}}
\begin{position}
% \begin{itemize}
This project was intended for my father, I set up a Raspberry pi zero as a security camera. I noticed that there was not enough memory to store all the videos so I created this project. I setup a AWS Linux server to backup the recordings from the security camera, and the script wipes all the recordings the camera I learned how to use rsync and cronnie how to schedule shell scripts and remotely backup files to another machine.
% \end{itemize}https://www.overleaf.com/project/5c3cda8d86f90560469d48be
\begin{itemize}
\item \textbf{Technology/Tools: cron, AWS, ssh, rsync, port forwarding}
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/byvictorrr/RPI-Camera-EC2-Backup
\end{itemize}
\end{position}

%Project 3
\employer{ByVictorrr}
\location{}
\title{\textbf{WindowsServerCalpolyStudents - For UNIX users  \hfill January 2019}}
\begin{position}
% \begin{itemize}
This was more of a tutorial for my fellow classmates that didnt have windows. Using an AWS EC2 windows server for school intended needs - EE software.
% \end{itemize}https://www.overleaf.com/project/5c3cda8d86f90560469d48be
\begin{itemize}
\item \textbf{Technology/Tools: gitbash, RPD - protocol, AWS, powershell}
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/byvictorrr/WindowServerCalpolyStudents
\end{itemize}
\end{position}

\section{CERTIFICATION}
\par
\normalfont{}
\\
\normalfont{}\textbullet{} \textbf{Computer Science - C++ Certificate of Achievement} by Canada College
\\ 
\textbullet{} \textbf{Engineering - Certificate of Achievement} by Canada College 


\section{RELEVANT\\COURSES}
\par

\normalfont{\textbullet{} Digital Design: github.com/byvictorrr/CPE133 }
\\
\normalfont{\textbullet{} Object Orientated Programming in Java: github.com/byvictorrr/CPE203 }
\\
\normalfont{\textbullet{} Object Orientated Programming in C++: https://github.com/ByVictorrr/Sudoku }
\\
\normalfont{\textbullet{} Data Structures in C++: https://github.com/ByVictorrr/GhostGame}
\\


\end{resume}
\(\)\end{document}
